output: github_document

## Neuralnet tutorial: basic concepts
Install the neuralnet package for R

```{r} 
install.packages('neuralnet')
library("neuralnet")
```

Define training set

```{r}
traininginput <-  as.data.frame(runif(50, min=0, max=100))
trainingoutput <- sqrt(traininginput)

trainingdata <- cbind(traininginput,trainingoutput)
colnames(trainingdata) <- c("Input","Output")
```

Train the neural network

```{r}
net.sqrt <- neuralnet(Output~Input,trainingdata, hidden=1, threshold=0.01)
print(net.sqrt)
```

Plot the neural network
```{r}
plot(net.sqrt)
```

Test the neural network on a validation set
```{r}
testdata <- as.data.frame((1:10)^2)
net.results <- compute(net.sqrt, testdata)
```

Examine properties and results
```{r}
ls(net.results)

print(net.results$net.result)
 
cleanoutput <- cbind(testdata,sqrt(testdata),
                         as.data.frame(net.results$net.result))
colnames(cleanoutput) <- c("Input","Expected Output","Neural Net Output")
print(cleanoutput)

```

This tutorial is based on the Gekkoquant tutorial on neural networks:
http://gekkoquant.com/2012/05/26/neural-networks-with-r-simple-example/

For additional resources, please see the Cambridge University short course on machine learning in R:
https://bioinformatics-training.github.io/
